---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# psymetadata

<!-- badges: start -->
<!-- badges: end -->

This data package provides open datasets from meta-analyses from different areas in psychological science. 

##  Installation

<!-- You can install the released version of glaxo from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("glaxo") -->
<!-- ``` -->

Until it's available on CRAN, you can install this package from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("josue-rodriguez/psymetadata")
```

## Adding a dataset
If you'd like to contribute a dataset to this package please do the following steps:

### 1)

Clone the repository to your local machine

### 2)

Clean your dataset so it is of type `data.frame` and has at least the following columns:

- `study_id`: unique id for study 
- `es_id`: unique id for effect size (if applicable)
- `yi`: effect size
- `vi`: variance of effect size

Column names should follow snake case formatting. This can easily be done by calling `janitor::clean_names()` on your data set. 

Feel free to include as many moderators or additional columns as you would like.


### 3)
Assign your dataset to an object with the format `[firstauthor][year]` and save it to the `data` folder with the format `[firstauthor][year].rda`, e.g.

```{r}
curry2015 <- cleaned_dataset
save(curry2015, file = "data/curry2015.rda")
```

where `curry2015` is a dataset originally collected from the publication Curry, Thompson, and Green (2015)

### 4)
Add a bibtex reference to the `inst/REFERENCES.bib` file. This can be easily obtained with a citation manager (e.g., Zotero) or with Google scholar 

### 5)
Document your dataset at the bottom of the `R/data.R` file. 

The documentation should roughly follow this format:

```
#' @title [Title]
#'
#' @description Results from [# of studies] studies, including [# of effect sizes] effect 
#' sizes ([type of effect size]), on [short description of studies] \insertCite{[cite key]}{psymetadata}.
#'
#' @format A data frame with [# of rows] rows and [# of columns] variables:
#'
#' * \code{yi}: [description]
#' * \code{vi}: [description]
#' * \code{study_id}: [description]
#' * \code{es_id}: [description]
#' * \code{moderator1}: [description]
#' * \code{moderator2}: [description]
#'
#'
#' @md
#'
#' @details Further details can be found at \href{[link]}{[link]}
#'
#' @usage data("[dataset]")
#'
#' @references
#' \insertAllCited{}
"[dataset]"
```

- Take a look at the `data.R` file for more examples

### 6)
Submit a pull request


